Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-05 draft/accordionComplexSurfaces.tex
figures kissing=crossing

\section{Introduction}
The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{BrustleDouvilleMousavandThomasYildirim}).

@@

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}
\begin{proof}
 \pierreguy{TO DO}
 \vincent{figure}
\end{proof}

@@

\begin{proof}
 \pierreguy{Picture No.4}
 \vincent{figure}
\end{proof}

@@

\subsection{The countercurrent order}
The countercurrent order was introduced in~\cite{McConville} for grids and defined in \cite{PaluPilaudPlamondon} for gentle algebras.
We now adapt it to locally gentle algebras.

>>>>

\section{Introduction}

The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also \cite{BrustleDouvilleMousavandThomasYildirim}).

@@

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}
\begin{proof}
 \pierreguy{TO DO}
\end{proof}

@@

\begin{proof}
See \fref{fig:kissings} and \fref{fig:kissingVSCrossing}.
\pierreguy{Complete this proof using the pictures.}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissings}}
	\caption{Two representations of a pair of kissing walks.}
	\label{fig:kissings}
\end{figure}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissingVSCrossing}}
	\caption{Kissing walks on the quiver~$\bar Q$ correspond to crossing curves on the surface~$\surface_{\bar Q}$.}
	\label{fig:kissingVSCrossing}
\end{figure}

\end{proof}

@@

\subsection{The countercurrent order}

The countercurrent order was introduced in~\cite{McConville} for grids and defined in \cite{PaluPilaudPlamondon} for gentle algebras.
We now adapt it to locally gentle algebras.
